Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-06-30 optim.tex
compiled files

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, colbacktitle=quarto-callout-note-color!10!white, breakable, opacityback=0, toptitle=1mm, leftrule=.75mm, titlerule=0mm, coltitle=black, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, rightrule=.15mm, arc=.35mm, toprule=.15mm, colback=white, bottomtitle=1mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, left=2mm]

>>>>

\begin{tcolorbox}[enhanced jigsaw, arc=.35mm, colback=white, toptitle=1mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, bottomtitle=1mm, coltitle=black, title={Algorithm: Jellyfish Optimizer Pseudo Code}, titlerule=0mm, rightrule=.15mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacitybacktitle=0.6, toprule=.15mm, leftrule=.75mm, left=2mm]
